Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-15 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses our
adapted extension of the Laplace Beltrami operator. Along with the
method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software blender.
\end{abstract}

@@

%i.e.= id est (esto es)
The LBO has desirable properties: the LBO points out to the direction
of the minimal surface area, minimizing the energy of the total surface
curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$ with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
or triangle $A\left(T_{N_{1}\left(v_{i}\right)}\right)$ to vertex $v_{i}$ in $M$   is.

@@

Applying the mean average area, according to \cite{Xiong2011}, from all
possible triangulations, as show in figure \ref{fig:quad_xiong}, the area for each quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$ is

@@

The vertices $V^{t+1}$ are enhanced, along their reverse curvature direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$ is the enhancement factor that supports negative
and positive values: negative for enhancement and positive for smoothing.

@@

\caption{\label{fig:Catmull_Clark}Left: Original Model,  color model
with Catmull-Clark Subdivision in green. Models with Laplacian smoothing: $\lambda=60.0$,
$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying curvature enhancement: $\lambda=-200.0$, $\lambda_{e}=12.0$
and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
\end{figure*}

@@

The Catmull-Clark subdivision transformation is used to smooth a surface,
as the limit of a sequence of subdivision steps\cite{Stam1998}. This
process is governed by a B-spline curve \cite{Loop1987}, performing a recursive subdivision transformation that refines the model into a linear interpolation
that approximates a smooth surface. The model smoothness is
automatically guaranteed \cite{DeRose1998}.

@@

Laplacian smoothing applied with simple subdivision may produce similar results to those obtained with Catmull-Clark, whose models are in average equal triangles, as shown in figure \ref{fig:Catmull_Clark}, green model. The one obtained with the Laplacian smoothing is shown in panel (c), (d)  and those curvature modified versions are in (d) and (f). As can be observed, different versions of the original sketch can be obtained by parameterizing a single model value, a great advantage of the presented method.  Figure \ref{fig:camello_enhanced} shows the generation of different versions of a camel according to the $\lambda$ parameter. In the top row,  it is shown the curvature enhancement results, as $\lambda$ becomes larger and negative, the resultant shape is observed as if the model would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter the larger the model feature enhancements. The bottom row of figure \ref{fig:camello_enhanced} shows the use of weighted vertex groups, specifying which areas will be enhanced. On the left, the enhancement of the camel legs produces an organic aspect, notice that the border is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model at left.
Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for the head
and neck.}
\end{figure}

@@

Under these conditions, the matrix at equation\ref{eq:TQLBO_Simple_Matrix}
is sparse since the number of neighbors per vertex, corresponding to
the number of data per row, is smaller compared to the total number of
vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
was used OpenNL which is a a library for solving sparse linear system.

>>>>

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses a
original extension of the Laplace Beltrami operator. Along with the
method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software blender.
\end{abstract}

@@

The LBO has desirable properties: the LBO points out to the direction
of the minimal surface area, minimizing the energy of the total surface
curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$.

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
or triangle $\ensuremath{A\left(T_{N_{1}\left(v_{i}\right)}\right)}$
to vertex $\ensuremath{v_{i}}$ in $M$ is.

@@

Applying the mean average area, according to \cite{Xiong2011}, from
all possible triangulations, as show in figure \ref{fig:quad_xiong},
the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
is

@@

The vertices $V^{t+1}$ are enhanced, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$

is the enhancement factor that supports negative and positive values:
negative for enhancement and positive for smoothing.

@@

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying curvature enhancement: (e) $\lambda=-200.0$,
$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
\end{figure*}

@@

The Catmull-Clark subdivision transformation is used to smooth a surface,
as the limit of a sequence of subdivision steps \cite{Stam1998}.
This process is governed by a B-spline curve \cite{Loop1987}, performing
a recursive subdivision transformation that refines the model into
a linear interpolation that approximates a smooth surface. The model
smoothness is automatically guaranteed \cite{DeRose1998}.

@@

Laplacian smoothing applied with simple subdivision may produce similar
results to those obtained with Catmull-Clark, whose models are in
average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
the Laplacian smoothing is shown in panel (c), (d) and those curvature
modified versions are in (e) and (f). As can be observed, different
versions of the original sketch can be obtained by parameterizing
a single model value, a great advantage of the presented method. Figure
\ref{fig:camello_enhanced} shows the generation of different versions
of a camel according to the $\lambda$ parameter. In the top row,
it is shown the curvature enhancement results, as $\lambda$ becomes
larger and negative, the resultant shape is observed as if the model
would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
The larger the $\lambda$ parameter the larger the model feature enhancements.
The bottom row of figure \ref{fig:camello_enhanced} shows the use
of weighted vertex groups, specifying which areas will be enhanced.
On the left, the enhancement of the camel legs produces an organic
aspect, notice that the border is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

@@

Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
is sparse since the number of neighbors per vertex, corresponding
to the number of data per row, is smaller compared to the total number
of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
was used OpenNL which is a a library for solving sparse linear system.

The curvature cannot be calculted at the border of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by

Desbrun et al. \cite{Desbrun1999}.
